SCPCL000822 - Validation of tumor cells

### 2024-06-12 analyses/cell-type-ewings/cell_type_annotations/SCPCS000490/SCPCL000822_tumor-cell-validation.Rmd
simplify case when statement

```{r}
# create a combined classification between inferCNV and copyKAT
# cells that are classified as tumor by both are kept as tumor
# classified by both as normal are normal 
# in between are classified as unknown
classification_df <- classification_df |> 
  dplyr::mutate(
    combined_cnv_classification = dplyr::case_when(
      # only tumor if both call tumor 
      cnv_proportion_classification == "Tumor" & copykat_classification == "Tumor" ~ "Tumor",
      # only normal if both call normal and/or reference
      cnv_proportion_classification == "Normal" & copykat_classification == "Normal" ~ "Normal",
      cnv_proportion_classification == "Reference" & copykat_classification == "Normal" ~ "Normal",
      # if normal/tumor mismatch set to unknown 
      cnv_proportion_classification == "Normal" & copykat_classification == "Tumor" ~ "Unknown",
      cnv_proportion_classification == "Tumor" & copykat_classification == "Normal" ~ "Unknown",
      cnv_proportion_classification == "Reference" &  copykat_classification == "Tumor" ~ "Unknown", 
      !is.na(cnv_proportion_classification) & is.na(copykat_classification) ~ "Unknown", 
      is.na(cnv_proportion_classification) & !is.na(copykat_classification) ~ "Unknown",
      is.na(cnv_proportion_classification) & is.na(copykat_classification) ~ "Unknown"
    ))
```

>>>>

```{r}
# create a combined classification between inferCNV and copyKAT
# cells that are classified as tumor by both are kept as tumor
# classified by both as normal are normal 
# in between are classified as unknown
classification_df <- classification_df |> 
  dplyr::mutate(
    combined_cnv_classification = dplyr::case_when(
      # only tumor if both call tumor 
      cnv_proportion_classification == "Tumor" & copykat_classification == "Tumor" ~ "Tumor",
      # only normal if both call normal and/or reference
      cnv_proportion_classification == "Normal" & copykat_classification == "Normal" ~ "Normal",
      cnv_proportion_classification == "Reference" & copykat_classification == "Normal" ~ "Normal",
      # if normal/tumor mismatch set to unknown 
      .default = "Unknown"
    ))
```
